The K2 Halo Photometry Campaign

### 2019-03-29 paper/ms.tex
paper updates

@@

\author[0000-0001-5222-4661]{Timothy R. Bedding}
\affiliation{Sydney Institute for Astronomy, School of Physics A28, The University of Sydney, NSW 2006, Australia}
\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}

\author[0000-0001-9879-9313]{Tabetha Boyajian}
\affiliation{Department of Physics and Astronomy, Louisiana State University, 202 Nicholsom Hall, Baton Rouge, LA 70803, USA}

@@

\noindent The weights are chosen to minimize the Total Variation

\begin{equation}
    TV \equiv \frac{\sum_i{|f_i - f_{i-1}|}}{\sum_i {f_i}},
\end{equation}

\noindent which can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length. TV is a convex objective function and has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd};][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.
% smear
This method differs from smear photometry \citep{Pope2016}, which uses collateral `smear' data to obtain a 1-D spatial profile with $\sim 1/1000$ of the flux on each CCD. While this has also been used for photometry of very bright stars, the `halo' method has the advantage of averaging over many more realizations of the K2 pointing systematics and permitting more significant calibration, achieving a generally higher photometric prevision.

@@

>>>>

\author[0000-0003-1453-0574]{Suzanne Aigrain}
\affiliation{Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK}

\author[0000-0001-5222-4661]{Timothy R. Bedding}
\affiliation{Sydney Institute for Astronomy, School of Physics A28, The University of Sydney, NSW 2006, Australia}
\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}
\author[0000-0001-9879-9313]{Tabetha Boyajian}
\affiliation{Department of Physics and Astronomy, Louisiana State University, 202 Nicholsom Hall, Baton Rouge, LA 70803, USA}

@@

@@

\noindent The weights are chosen to minimize the a modified Total Variation

\begin{equation}
    TV \equiv \frac{\sum_i{|f_i - f_{i-l}|}}{\sum_i {f_i}},
\end{equation}

\noindent which for $l = 1$ is the standard Total Variation and can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length. We introduce a lag parameter $l$ in order to allow for flexibility in modelling systematics occurring at different timescales from cadence-to-cadence, and we investigate its effects below. TV is a convex objective function and has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd};][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.
% smear
This method differs from smear photometry \citep{Pope2016}, which uses collateral `smear' data to obtain a 1-D spatial profile with $\sim 1/1000$ of the flux on each CCD. While this has also been used for photometry of very bright stars, the `halo' method has the advantage of averaging over many more realizations of the K2 pointing systematics and permitting more significant calibration, achieving a generally higher photometric prevision.

@@

% benchmarking with lags and
